%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Command for printing skill overview bubbles
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Software}\\\textbf{Development},
        \textbf{Full Stack}\\\textbf{Web Dev},
        \textbf{~~~~~OOP~~~~~~},
        \textbf{Mobile}\\\textbf{Dev},
        \textbf{Machine}\\\textbf{Learning},
        \textbf{~~Big Data~},
         \textbf{Research}
    }
}

% Programming skill bars
\programming{ {Scala  $\textbullet$ Python  $\textbullet$ C\# / 3.9}, {
		C $\textbullet$ C++  $\textbullet$ PHP  / 4.9}, {Java $\textbullet$ JS /5.5 }}

% Projects text


%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Ehab Qadah} % Your name
\cvjobtitle{ Software  Engineer } % Job
% title/career
\cvmail{ehabqadah@gmail.com} % Email address
\cvlinkedin{/in/ehabqadah/}
\cvgithub{ehabqadah}
\cvnumberphone{49 1729151241} % Phone number
\cvsite{ehab-qadah} % Personal website


%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
    	{2015 - now}
        {}
        {M.Sc.  in  Computer Science}
        {\href{https://www.uni-bonn.de/}{\textbf{University of Bonn, Germany}}}
        {}
        {}
	\twentyitem
    	{2009 - 2013}
		{}
        {B.Sc. in Computer Systems Engineering }
        {\href{https://www.birzeit.edu/en}{\textbf{Birzeit University,  Palestine}}}
        {}
        {}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}

%\section{Publications}


%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
	
	\twentyitem
	{May 2017 -}
	{Present}
	{Reseach Assistant}
	{\href{https://www.iais.fraunhofer.de/?L=1}{\large\textbf{Fraunhofer IAIS}, Germany}}
	{}
	{\begin{itemize}
			\item Involved in building stream processing pipelines on a Kafka cluster using Flink in the context of the \href{http://www.datacron-project.eu/}{datAcron} project.
			
			\item Working on my master \textbf{thesis}: "Distributed Online Learning for Large-scale Pattern Prediction over Real-time Event Streams".
	\end{itemize}}
\\
		\twentyitem
	{2016 - 2017}
	{}
	{Teaching Assistant}
	{\href{https://www.kdml.iai.uni-bonn.de/teaching/winter-2016-17}{\large\textbf{University of Bonn}, Germany}}
	{}
	 {\begin{itemize}
			\item Teaching and correcting exercises and exams for the Intelligent Learning ​ And Analysis Systems: Machine Learning course  MA-INF 4111, winter semester 2016/17.
	\end{itemize}}


        \\
	\twentyitem
    	{March 2016 -}
		{March 2017}
        {Front-End Developer (part-time)}
        {\href{https://twitter.com/TROIUS_DIGITAL}{\large\textbf{TROIUS DIGITAL}, Germany}}
        {}
        {
        {\begin{itemize}
        \item Designed and developed web applications (front-end) using HTML, CSS, Javascript, JQuery and React.
        \item Built and maintained web services using Node.js and PHP.
    \end{itemize}}
        }
    \\   
    \twentyitem
   		{Sep 2015 -}
		{Dec 2016}
        {R\&D Engineer}
        {\href{https://www.freightos.com/}{\large\textbf{Freightos (Tradeos LTD )}, Palestine Office}}
        {}
        {
        {\begin{itemize}
        \item Developed software components based on  GWT and Google AppEngine to provide Java web and back-end solutions.
        \item Experience in using Google's DataStore, Memcache, CloudSQL and BigQuery API.
        \item Participated in code reviews, team design sessions and contributes to the team’s strategy and process improvements.
        
        
    \end{itemize}}
        }
     \\
     \twentyitem
   		{Aug 2012 -}
		{Sep 2014}
        {Software Engineer}
        {\href{http://www.exalt-tech.com/about/}{\large\textbf{EXALT Technologies Ltd}, Palestine}}
        {}
        {
        \begin{itemize}
        \item Web and desktop applications development using ASP.NET C\#.
        \item Designed and developed Android applications. 
        \item Participated in full development lifecycle from concept to deployment.
        
    \end{itemize}
    	}
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

\section{Technical  Skills}
\begin{twenty} % Environment for a list with descriptions
	\twentyitem
	{}
	{}
	{Programming Languages}
	{}
	{}
	{ \begin{itemize}
			\item Java, C/C++, C\# and  Python.	\\	
	\end{itemize}}
		\twentyitem
	{}
	{}
	{Big Data Technologies}
	{}
	{}
	{ \begin{itemize}
			\item Apache Flink,  Apache
			Spark and Apach Kafka.	\\	
	\end{itemize}}

		\twentyitem
{}
{}
{Scripting languages}
{}
{}
{ \begin{itemize}
		\item Shell Scripts, VHDL, VBScript and Assembly.	\\	
\end{itemize}}



	\twentyitem
{}
{}
{Others}
{}
{}
{ \begin{itemize}
		\item Databases: MySQL, MongoDB and SQLlite.
		\item Git, SVN, Maven, Gradle, webpack and Docker.
		\item Excellent Computer Science fundamentals, object-oriented design, data structures, algorithm design, problem solving, and complexity analysis.
		
		
\end{itemize}}
\end{twenty}
\end{document} 
